Data Builder

### 2019-04-04 notebooks/data_builder.Rmd
prose in results up to parity, working out L2 now. will also get plots and data for function-level polymorphism

# display
L0_poly_sig[1:10,] %>% ready_print_count_fun %>% xtable %>% print(include.rownames=F)
L1_poly_sig[1:10,] %>% ready_print_count_fun %>% xtable %>% print(include.rownames=F)
```

@@

data.frame(`Signature Type`=c("Monomorphic", "Total Seen"), Count=paste0(c(mono_L0_funs_c/1000, tot_L0_funs/1000) %>% as.integer, "K"), Percentage=c(paste0(round(mono_L0_funs_c/tot_L0_funs * 100, 1), "%"), "---")) %>% xtable %>% print(include.rownames=F)
```

@@

@@

>>>>

# display all args 
L0_arg_sig_c[1:10,] %>% ready_print_count_fun %>% xtable %>% print(include.rownames=F)
L1_arg_sig_c[1:10,] %>% ready_print_count_fun %>% xtable %>% print(include.rownames=F)

# display poly
L0_poly_sig[1:10,] %>% ready_print_count_fun %>% xtable %>% print(include.rownames=F)
L1_poly_sig[1:10,] %>% ready_print_count_fun %>% xtable %>% print(include.rownames=F)
```

@@

data.frame(`Signature Type`=c("Monomorphic", "Total Seen"), Count=paste0(c(mono_L0_funs_c/1000, tot_L0_funs/1000) %>% as.integer, "K"), Percentage=c(paste0(round(mono_L0_funs_c/tot_L0_funs * 100, 1), "%"), "---")) %>% xtable %>% print(include.rownames=F)

data.frame(`Signature Type`=c("Monomorphic", "Total Seen"), Count=paste0(c(mono_L1_funs_c/1000, tot_L1_funs/1000) %>% as.integer, "K"), Percentage=c(paste0(round(mono_L1_funs_c/tot_L1_funs * 100, 1), "%"), "---")) %>% xtable %>% print(include.rownames=F)
```

@@

# L1
data.frame(`Signature Type`=c("Monomorphic", "Total Seen"), Count=c(L1_arg_sig_c$count %>% sum - L1_poly_sig$count %>% sum, L1_arg_sig_c$count %>% sum), Percentage=c(paste0(round(100 * (1 - (L1_poly_sig$count %>% sum / L1_arg_sig_c$count %>% sum)), 1), "%"), "---")) %>% xtable %>% print(include.rownames=F)

@@

```{r}
prim_scal <- c("sD", "sL", "sC", "sX", "sI", "sR")
# compute scalars 
L1_sc_c <- L1_arg_sig_c[unlist(lapply(L1_arg_sig_c$arg_sig, function(s) nchar(s) == 2 && substr(s, 1, 1) == "s")), ]
L1_sc_c <- L1_sc_c[L1_sc_c$arg_sig %in% prim_scal,]
num_scal <- sum(L1_sc_c$count)

percent_scalar_mono <- round( 100 * num_scal / sum(L1_arg_sig_c$count), 1)
```
